\documentclass[acmsmall]{acmart}
\usepackage{indentfirst}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}


\begin{document}


\title{Automated Generation of Design Models from Source Code}


\author{yu Chen}
\author{shaoke Cui}
\author{xiaolei Gu}
\author{zeyu Han}
\author{wenfei Shi}
\author{weichen Zhang}


\begin{abstract}
Automated generation of design models from source code have shown promise as a cost-effective means for precise understanding of the system. In this paper, we conclude several challenges still exist in this field and find some research results corresponding to these challenges.
\end{abstract}


\maketitle

\section{Introduction}
{\itshape Automated Generation of Design Models from Source Code} is a specific field of reverse engineering. It aims at generating design models from source code. The design models it generates can help developers understand the whole system, help evolve the system and check whether some behaviors of the system has errors. Since the scale and complexity of the system is increasing constantly, this technology becomes more and more significant.


According to the papers we have read, we have found some challenges exist in this field. The main aim of generating design models from source code is to help developers to understand how the system runs. So extracting business rules from source code is one of the basic challenge should meet. Also the design models should be smartly visualized to help developers have a specific understanding. Besides these basic needs, because of the large scale and complexity, it's time-consuming to finish this work. Complexity also causes possible information loss through transformation. Finally,considering multi-language program, the tools for generating design models should accept multi-language or transform multi-language to its own input language.

\section{Review Method}

\subsection{Research questions}
According to the main challenge mentioned above, we have raised five specific research questions.
\begin{itemize}
\item  How to extract the business logic from the source code
\item  How to visualize the design model for easier understanding
\item  How to solve the problem of time-consuming model construction and state explosion
\item  How to avoid the possible information loss when inferring relationships by attribute definition
\item  How to build tools that accept multi languages
\end{itemize}

\subsection{Search process}


\section{Review Result}


\section{Conculsion}


\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

\section{Appendix}


\end{document}
\endinput